Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-06-16 sas2015/content/impl.tex
applying Frank's comments

We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
Our implementation analyzes JVM bytecode compiled from input programs written
in Java.
%
We use WALA~\cite{fink2012wala} to retrieve information about an input program, such 
as its control-flow supergraph and the set of receivers and their types.
Since WALA does not contain an implementation of the IDE algorithm,
we implemented it from scratch.
We will submit our implementation to the artifact evaluation committee, and are also 
working on contributing our infrastructure to WALA.

@@

@@

\commentout{
The artifact of our implementation can be used to solve any IFDS problem. In the presence of correlated calls, the result of the correlated-calls analysis can be more precise than the result obtained with an IFDS solver.
}

>>>>

We implemented the correlated-calls analysis in Scala~\cite{odersky2004overview}. 
Our implementation analyzes JVM bytecode compiled from input programs written
in Java.
%
We use WALA~\cite{fink2012wala} to retrieve information about an input program, such 
as its control-flow supergraph and the set of receivers and their types.
Since WALA does not contain an implementation of the IDE algorithm,
we implemented it from scratch;
%We will submit our implementation to the artifact evaluation committee, 
we are working on contributing our infrastructure to WALA.

@@

The equivalence analysis is there for two reasons: 
(i)  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem, and 
(ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis\footnote{
We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.
}.

@@
